Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-05-31 main_paper.tex
Make minor wording tweak in introduction
The wording 'especially promising' seemed to be a bit too much of a
claim, so I've changed it to 'promising.'

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
especially promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodates in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and two limitations should be noted in particular. First, the confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Second, the bootstrap proposed in this paper imposes local
homoskedasticity and can perform poorly when the DGP exhibits significant
heteroskedasticity. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model and uniform kernel. So the practical benefits
of using the bootstrap in this context are relatively limited. Relaxing these
limitations is the subject of ongoing research by the authors.

>>>>

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodates in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and two limitations should be noted in particular. First, the confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Second, the bootstrap proposed in this paper imposes local
homoskedasticity and can perform poorly when the DGP exhibits significant
heteroskedasticity. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model and uniform kernel. So the practical benefits
of using the bootstrap in this context are relatively limited. Relaxing these
limitations is the subject of ongoing research by the authors.
